Regression Cube Analysis of Cohort Study Data

### 2015-06-15 draft.tex
sorted reviews, minor changes

%% indicate IEEE Member or Student Member in form indicated below
\author{Paul Klemm, Kai Lawonn, Sylvia Gla{\ss}er, Uli Niemann, Katrin Hegenscheid, Henry V{\"o}lzke, Bernhard Preim}
\authorfooter{
%% insert punctuation at end of each item
\item
 Paul Klemm, Kai Lawonn, Sylvia Gla{\ss}er, Uli Niemann, Bernhard Preim are with Otto-von-Guericke University Magdeburg, Germany. E-mail: \{klemm,lawonn,glasser,uli.niemann,preim\}@ovgu.de
\item
 Katrin Hegenscheid, Henry V{\"o}lzke are with Ernst-Moritz-Arndt University Greifswald, Germany. E-mail: \{katrin.hegenscheid,voelzke\}@uni-greifswald.de
}

>>>>

%% indicate IEEE Member or Student Member in form indicated below
\author{Paul Klemm, Kai Lawonn, Sylvia Gla{\ss}er, Uli Niemann, Katrin Hegenscheid, Henry V{\"o}lzke, Bernhard Preim}
\authorfooter{
%% insert punctuation at end of each item
\item
 Paul Klemm, Sylvia Gla{\ss}er, Uli Niemann, Bernhard Preim are with Otto-von-Guericke University Magdeburg, Germany. E-mail: \{klemm,lawonn,glasser,uli.niemann,preim\}@ovgu.de
\item
 Katrin Hegenscheid, Henry V{\"o}lzke are with Ernst-Moritz-Arndt University Greifswald, Germany. E-mail: \{katrin.hegenscheid,voelzke\}@uni-greifswald.de
\item
 Kai Lawonn is with Otto-von-Guericke University Magdeburg, Germany and Delft University of Technology, Delft, Netherlands. E-mail: lawonn@ovgu.de
}
